\documentclass[draft=false]{deedy-resume-openfont}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LAST UPDATED DATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Usama}{Tahir}{ 
    \urlstyle{same}
    \url{}
    \href
        {mailto:14beseutahir@seecs.edu.pk}{14beseutahir@seecs.edu.pk}  |  (+92)3065150502\\
        \vspace{0.5cm}
        \location{
        \subsection{Objective:}
        I aim to excel in software design and development in a research oriented and dynamic workplace where I can grow professionally and personally while using my skills for the success of the organization.
    }
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.39\textwidth} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{0.5cm}
\section{Education}
\vspace{0.1cm}
\subsection{National University of Science and Technology, Pakistan}
\vspace{0.1cm}
\descript{BE in Software Engineering}
\vspace{0.1cm}
\location{June 2014, June 2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.5cm}
\section{Links}
\vspace{0.1cm}
% Github: href{https://github.com/Usama-Tahir}{\bf Usama-Tahir}
Github:// \href{https://github.com/Usama-Tahir}{\bf Usama-Tahir}\\
LinkedIn://  \href{https://www.linkedin.com/in/usama-tahir-101/}{\bf usama-tahir-101}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.5cm}
\section{Skills}
\subsection{Programming}

\vspace{0.2cm}\
\location{Front End Dev:}
\vspace{0.3cm}
\textbullet{}Reactjs{} {} {} {} {} {} {} {} {} {} {} {} {} {} \textbullet{}Redux{} {} {} {} {} {} {} {} {} {} {} {} {} {}
\vspace{0.3cm}\textbullet{}Material Ui Design{} {} {} {} {} {} {} {} {} {} {} {} {} {}
\textbullet{}JavaScript/ES6/ES7{} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} \vspace{0.3cm}\textbullet{}HTML/CSS \textbullet{}TypeScript{} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} \textbullet{}Bootstrap\\
\vspace{0.4cm}
\location{Back End Dev:}
\vspace{0.3cm}
\textbullet{}Node.js{} {} {} {} {} {} {} {} {} {} {} {} {} {} \textbullet{}Express.js{} {} {} {} {} {} {} {} {} {} {} {} 
\vspace{0.3cm}\textbullet{}Laravel{} {} {} {} {} {} {} {} {} {} {} {} {} {}
\textbullet{}Nest.js{} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {} {}\vspace{0.3cm}
\textbullet{}Serverless{} {} {} {} {} {} {} {} {} {}  \textbullet{}AWS lambdas{} {} {} {} {} {} {} {} {} {} {} \textbullet{}GraphQL{} {} {} {} {} {} {} {} {} {} {}  \vspace{0.3cm}\textbullet{}Rest Apis{} {} {} {} {} {} {} {} {} {} {} {}
 \textbullet{}MicroServices\\
 \vspace{0.4cm}
 \location{Languages}
 \vspace{0.3cm}
 \textbullet{}Python{}{} {} {} {} {} {} {} {} {} {} {} {} {} 
 {} {} {} \textbullet{Typescript}{} {} {} {} {} {} {} {} {} {} {} {} {}\vspace{0.3cm}\textbullet{}C++{} {} {} {} {} {} {} {} {} {} {} {} {} {}
 \textbullet{}Java{} {} {} {} {} {} {} {} {} {} {} {} {} {}\textbullet{}JavaScript/ES6/ES7\\
 \vspace{0.4cm}
%  \location{Libraries and Tools:}
%  \vspace{0.3cm}
%  \textbullet{}Async.js{} {} {} {} {} {} {} {} {} {} {} {} {} {} {}\textbullet{}Lodash.js{} {} {} {} {} {} {} {} {} {} {} {} {} {}\vspace{0.3cm}\textbullet{}VS Code {} {} {} {} {} {} {} {} {} {} {} {}
%  \textbullet{}Linux {} {} {} {} {} {} {} {} {} {} {} {}\\
\vspace{0.4cm}
\location{Databases:}
\vspace{0.3cm}
\textbullet{}MongoDB{} {} {} {} {} {} {} {} {} {} 
\textbullet{}Firestore {} {} {} {} {} {} {} {} {} {} {} {} {} {}\vspace{0.3cm}\textbullet{}MySQL {} {} {} {} {} {} {} {} {} {} {} {} {} {}
\textbullet{}PostgreSQL {} {} {} {} {} {} {} {} {} {} {} {} {} {}\\
\vspace{0.4cm}
\location{Cloud Platforms}
\vspace{0.3cm}
\textbullet{}Amazon Web Services (AWS) {} {} {} {} {} {} {} {}  {} {} \textbullet{} Firebase {} {} {} {} {} {} {} {} {} {} {} {} {}
 
\sectionsep
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % INTERESTS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{0.5cm}
% \section{INTERESTS}
% \vspace{0.1cm}
% \textbullet{}Problem Solving\\
% \vspace{0.1cm}
% \textbullet{}Reading \& Teaching\\
% \vspace{0.1cm}
% \textbullet{}Squash \& Table Tennis\\
% \vspace{0.1cm}
% \textbullet{}Horse Riding \& Fitness



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.58\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.5cm}
\section{Experience}

\runsubsection{CreativeMorph}
\descript{Full Stack JavaScript Developer}
\location{19 June 2018 - Current | Lahore, Pakistan}
\vspace{0.5cm}
\begin{tightemize}
\item Hands on Node.js, Express.js and Nest.js.
\item Hands on Serverless and AWS lambdas.
\item Hands on Micro Services.
\item Hands on frontend libraries like React.js, 
\end{tightemize}
\sectionsep

\runsubsection{Researcher at Media lab, NUST}
\descript{Research Intern }
\location{Summer 2017 | Islamabad, Pakistan}
I worked as a Research Intern in Media lab, Nust helping MS students in their research.
\begin{tightemize}
\item Hands on Maya 3D.
\item Hands on Research methodologies
\item Hands on Web Scrapping and Web Crawlers using Python
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.1cm}
\section{Projects}

\custombold{Therify.com}\\An AA/NA ATTENDANCE APP for the automating the attendance of AA/NA meetings. I worked on the back-end for the mobile app and admin dashboard. The admin dashboard was built in React.js. For backend, Node.js with serverless architecture was used. \\
\vspace{0.2cm}
website link: \href{http://therify.com/}{\bf therify.com} \\
\vspace{0.2cm}
\custombold{Bitfinding.com}\\ Worked as a Full Stack JavaScript Developer and developed the back-end API and front-end app. The tech stack used included React.js for front-end and Nest.js for the back-end. PostgreSQL was used with TypeOrm for database.\\
Demo Link: \href{https://apptest.bitfinding.com}{\bf apptest.bitfinding.com}\\
\vspace{0.2cm}
\custombold{Worky}\\ A web app for evaluating employees performance based on different stats available. I am working as a Full Stack Developer on this project. The back-end is mainly being written in Node.js and the front-end app is being built in React.js .\\
\vspace{0.2cm}
\custombold{METER- PWA}\\ Developed a PWA website in React.js for onboarding. Also contributed to the back-end. Now I have started working on a decentralized web app for the same organization. \\
website link: \href{https://www.meter.io/}{meter.io}\\
demo link: \href{http://dfinlab.s3-website-us-east-1.amazonaws.com/registration}{dfin-pwa.com}\\
\vspace{0.2cm}
\custombold{Data Compression Algorithms Implementation} Implemented Data Compression algorithms like LZW and HUFFMAN. They were implemented in Java.
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}